---
title: "hydflood3"
author: "Arnd Weber"
date: "`r Sys.Date()`"
output:
  html_vignette:
    toc: yes
    toc_depth: 3
bibliography: ../inst/REFERENCES.bib
csl: ../vignettes/apa_modified.csl
vignette: |
  %\VignetteIndexEntry{hyd1d} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.align="center",
    fig.width = 7,
    fig.height = 4, 
    root.dir = "vignettes"
)
```

<!-- Indent in html version TOC
     obtained from: 
     https://stackoverflow.com/questions/46201753/rmarkdown-indentation-of-toc-items-in-html-output
     -->

<script>
$(document).ready(function() {
  $items = $('div#TOC li');
  $items.each(function(idx) {
    num_ul = $(this).parentsUntil('#TOC').length;
    $(this).css({'padding-left': num_ul * 5px, 'box-shadow': none});
  });

});
</script>

<!-- numbering for figures and tables-->

```{r captions, echo = FALSE, error = FALSE, warning = FALSE, message = FALSE, include = FALSE}
# standard library path for the installed local packages
R_version <- paste(sep = ".", R.Version()$major, R.Version()$minor)
lib <- paste0("~/R/", R_version, "/")
require(hyd1d, lib.loc = lib)
require(hydflood3, lib.loc = lib)

# set english locale to produce english plot labels
Sys.setlocale(category = "LC_MESSAGES", locale = "en_US.utf8")

# Determine the output format of the document
outputFormat <- knitr::opts_knit$get("rmarkdown.pandoc.to")

# Figure and Table Caption Numbering, for HTML do it manually
capTabNo <- 1
capFigNo <- 1

# Function to add the Table Number
capTab <- function(x){
    if(outputFormat == 'html'){
        x <- paste0("**Tab. ", capTabNo, "**: ", x)
        capTabNo <<- capTabNo + 1
    }
    return(x)
}

# Function to add the Figure Number
capFig <- function(x){
    if(outputFormat == 'html'){
        x <- paste0("**Fig. ", capFigNo, "**: ", x)
        capFigNo <<- capFigNo + 1
    }
    return(x)
}
```

<BR>

# Purpose

**hydflood3** is an R package designed to compute flood extent and duration 
along the German federal waterways Elbe and Rhine.

<BR>

# Use

## Installation

The package **hydflood3** is not available from CRAN at the moment. To install 
the recent developmental version from the GitBucket server of the Federal Institute 
of Hydrology (BfG) execute the following commands: 

```{r install_git, eval = FALSE}
install.packages("devtools")
library(devtools)
devtools::install_git("git://apps.bafg.de/gitbucket/webera/hydflood3.git")
```

Afterwards **hydflood3** can be loaded like every other R package with the 
following command: 

```{r library, eval = TRUE, echo = FALSE, error = FALSE, warning = FALSE, message = FALSE}
# standard library path for the installed local packages
R_version <- paste(sep = ".", R.Version()$major, R.Version()$minor)
lib <- paste0("~/R/", R_version, "/")
library(hydflood3, lib.loc = lib)
```

```{r library_print, eval = FALSE, echo = TRUE}
library(hydflood3)
```

# References

---
nocite: | 
  @brunotte_flussauen_2009
  @bfn_auenzustandsbericht_2009
...

